Component response rate variation drives stability in large complex systems

### 2018-04-19 ms.Rmd
Re-run with more iters

---
title: "Stability concerns in random matrices"
author: "Brad Duthie"
bibliography: references.bib
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

```{r, eval = TRUE, echo = FALSE}
eig_cloud <- eigen_cloud(sp = 20, iters = 1000);
Pr_D0     <- sum(eig_cloud$d0[,1] < 0) / length(eig_cloud$d0[,1]);
Pr_D1     <- sum(eig_cloud$d1[,1] < 0) / length(eig_cloud$d1[,1]);
Pr_D2     <- sum(eig_cloud$d2[,1] < 0) / length(eig_cloud$d2[,1]);
Pr_D3     <- sum(eig_cloud$d3[,1] < 0) / length(eig_cloud$d3[,1]);
Pr_D4     <- sum(eig_cloud$d4[,1] < 0) / length(eig_cloud$d4[,1]);
```

>>>>

---
title: "Component response rate variation drives stability in large complex systems"
author: "Brad Duthie"
bibliography: references.bib
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

```{r, eval = TRUE, echo = FALSE}
eig_cloud <- eigen_cloud(sp = 20, iters = 10000);
Pr_D0     <- sum(eig_cloud$d0[,1] < 0) / length(eig_cloud$d0[,1]);
Pr_D1     <- sum(eig_cloud$d1[,1] < 0) / length(eig_cloud$d1[,1]);
Pr_D2     <- sum(eig_cloud$d2[,1] < 0) / length(eig_cloud$d2[,1]);
Pr_D3     <- sum(eig_cloud$d3[,1] < 0) / length(eig_cloud$d3[,1]);
Pr_D4     <- sum(eig_cloud$d4[,1] < 0) / length(eig_cloud$d4[,1]);
```
